Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: pass on rewards

This setup was chosen as it presents a challenging coordination problem that requires agents to learn both individual target-seeking behaviors and collaborative strategies for reducing the overall retrivial time, 
offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
\subsection{Reward}
One of the most important aspects in MARL is how the reward signal that the agents use to 
  learn is defined.
%
In particular, we have defined a reward function composed of many subcomponents.

\paragraph{Collisions} Agents are penalized when their action area intersect. 
  \[ \psi = \begin{cases}
    0 & \text{if no intersections} \\
    -2 \cdot |I_a| & \text{otherwise}
  \end{cases} \]
  Where $I_a$ is the set of agents with intersecting action area.

\paragraph{Time step} Agents are penalized at each time step by a constant value $\sigma$ defined as
    an hyperparameter.
    \[ \zeta = - \sigma \]

\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items.
    \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
    Where $p_a^t$ is the position of the agent $a$ at time t (similarly for $p_i^{t}$ regarding items),
    $\delta$ is a scalar hyperparameter used to tune the importance of this component and
    $V_{items}$ is the set of visible items.
\paragraph{Moving away from agents} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$).
    \[ \chi = \frac{1}{2|N_{a_i}|} \cdot \sum_{a_j \in N_{a_i}} d(p_{a_i}^{t+1}, p_{a_j}^{t+1}) - d(p_{a_i}^{t}, p_{a_j}^{t}) \]

\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$) is the set of collected items), 
    whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 
    to develop cooperative behaviors.
    \[ \rho = 100 \cdot |C_i| \]

>>>>

This setup was chosen as it presents a challenging coordination problem that requires agents to learn both individual target-seeking behaviors and collaborative strategies for reducing the overall retrivial time, 
offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
\subsubsection{Reward function}
In the proposed environment, we design a reward function that both consider the individual performance of each agent (e.g., avoid collision) and the global performance of the team (e.g., collect items in the shortest time possible).
In the following, we describe the components of the reward function:
\paragraph{Collisions} Agents are penalized when their action area intersect. This penalty is proportional to the number of agents involved in a collision:
  \[ \psi = \begin{cases}
    0 & \text{if no intersections} \\
    -2 \cdot |I_a| & \text{otherwise}
  \end{cases} \]
where $I_a$ is the set of agents with intersecting action area.

\paragraph{Time step} Agents are penalized at each time step by a constant value $\sigma$ defined as
    an hyperparameter, to encourage them to complete the task as quickly as possible.
    \[ \zeta = - \sigma \]

\paragraph{Moving towards items} Each agent $a$ is rewarded if it moves towards one of the visible target items, discouraging agents from wandering aimlessly.
    \[ \xi = (max_{i \in V_{items}} d(p_a^{t+1}, p_i^{t+1}) - d(p_a^{t}, p_i^{t})) \cdot \delta\]
    Where $p_a^t$ is the position of the agent $a$ at time t (similarly for $p_i^{t}$ regarding items),
    $\delta$ is a scalar hyperparameter used to tune the importance of this component and
    $V_{items}$ is the set of visible items.
\paragraph{Moving away from agents} Each agent $a_i$ is rewarded if it increases the distance from its neighbors ($N_{a_i}$). This strategy encourages agents to avoid clustering and explore the environment more effectively.
    \[ \chi = \frac{1}{2|N_{a_i}|} \cdot \sum_{a_j \in N_{a_i}} d(p_{a_i}^{t+1}, p_{a_j}^{t+1}) - d(p_{a_i}^{t}, p_{a_j}^{t}) \]

\paragraph{Collecting items} Each agent is rewarded for any collected visible items ($C_i$ is the set of collected items), 
    whether the item was collected by  the agent itself or by another agent, this strategy encourages agents 
    to develop cooperative behaviors.
    \[ \rho = 100 \cdot |C_i| \]
